But I can't preregister my research: Improving the reproducibility and transparency of ecology and conservation with adaptive preregistration for model-based research

### 2024-09-25 _analysis/ms.qmd
Add quarto preprint output extension and update YAML
update prereg template table organisation

@@

  pdf: default

@@

>>>>

  preprint-typst:
    fontsize: 11pt
    mainfont: Libertinus Serif 

@@

  preprint-docx:
    toc: false
    number-sections: true
    highlight-style: github

@@

```{r}
#| label: preregistration-template-final
#| eval: true
#| echo: false
#| message: false

library(tidyverse)
library(gt)
library(gtExtras)

prereg_tbl_data <- 
  readr::read_csv(
    here::here("outputs/quarto_preregistration_template.csv")) %>% 
  drop_na(phase) %>% 
  mutate(across(everything(), ~ stringr::str_remove_all(.x, "\\*")),
         phase = forcats::as_factor(phase), 
         step = forcats::as_factor(step), 
         substep = forcats::as_factor(substep)) %>% 
  mutate(phase_id = cur_group_id(), .by = phase) %>% 
  group_by(pick(starts_with("phase"), 
                starts_with("step"), 
                starts_with("substep"),
                -ends_with("_id")), 
           preregistration_item) %>% 
  reframe(preregistration_subitem = list(preregistration_subitem), 
          subitem_na = map_lgl(preregistration_subitem, rlang::is_na)) %>% 
  group_by(pick(starts_with("phase"), 
                starts_with("step"), 
                starts_with("substep"),
                -ends_with("_id"), 
                "subitem_na")) %>% 
  reframe(preregistration_item = 
            case_when(subitem_na ~ list(preregistration_item), 
                      .default = map(preregistration_item, list)),  
          preregistration_subitem = 
            case_when(subitem_na ~ list(NA), 
                      .default = map(preregistration_subitem, 
                                     ~ gluedown::md_list(.x, type = "bullet", marker = "-")))) %>% 
  rowwise() %>% 
  mutate(preregistration_item = 
           list(gluedown::md_list(preregistration_item, type = "bullet", marker = "-"))) %>% 
  arrange(phase, step, substep) %>% 
  ungroup %>%  
  mutate(step_id = 1:n(), 
         step = case_when(step_id == 1 ~ step, .default = NA),
         step_description = case_when(step_id == 1 ~ step_description, .default = NA),
         .by = c(phase, step)) %>% 
  mutate(substep_id = 1:n(), 
         substep = 
           case_when(substep_id == 1 ~ substep, 
                     .default = NA),
         substep_description = 
           case_when(substep_id == 1 ~ substep_description, 
                     .default = NA),
         .by = c(phase, step, substep)) %>% 
  mutate( phase = gluedown::md_bold(phase),
          phase_description = gluedown::md_italic(phase_description),
          across(ends_with("_id"), as.numeric)) %>% 
  rowwise() %>% 
  mutate(step = 
           forcats::fct_relabel(step, 
                                .fun = ~ if(!rlang::is_na(.x)) gluedown::md_bold(.x)),
         substep = 
           forcats::fct_relabel(substep, 
                                .fun = ~ if(!rlang::is_na(.x)) gluedown::md_bold(.x)),
         step_description = 
           forcats::fct_relabel(step_description, 
                                .fun = ~ if(!rlang::is_na(.x)) gluedown::md_italic(.x)),
         substep_description = 
           forcats::fct_relabel(substep_description, 
                                .fun = ~ if(!rlang::is_na(.x)) gluedown::md_italic(.x))) %>% 
  ungroup %>% 
  select(starts_with("phase"), 
         starts_with("step"), 
         starts_with("substep"), 
         ends_with("_item"), 
         ends_with("subitem"), 
         everything(),
         -subitem_na)

prereg_tbl_data %>% 
  gt::gt(
    groupname_col = c("phase", "phase_description"),
    rowname_col = "step",
    row_group.sep = ": ") %>% 
  gt::cols_hide(ends_with("_id")) %>% 
  gt::sub_missing(missing_text = "") %>% 
  gt::cols_merge(columns = c("step", "step_description"),
                 pattern =   "{1}\n {2}",) %>% 
  gt::cols_merge(columns = c("substep", "substep_description"),
                 pattern = "{1}\n {2}") %>% 
  gt::text_transform(fn = gt::md, 
                     locations = gt::cells_stub()) %>%
  gt::text_transform(fn = function(x) map(x, gt::md), 
                     locations = gt::cells_row_groups()) %>% 
  gt::text_transform(fn = gt::md, gt::cells_body()) %>% 
  gt::sub_missing(missing_text = "") %>% 
  gt::cols_align(align = "left") %>% 
  # gt::cols_label(substep = "Substep") %>% 
  # gt::tab_spanner(columns = starts_with("preregistration_item"), 
                  # label = "Preregistration Items", gather = TRUE) %>% 
  gt::tab_options(column_labels.hidden = TRUE, table.width = 10,table.font.size = 10) %>%
  gt::opt_stylize(2,color = "cyan") %>% 
  gt::tab_style(style = gt::cell_text(v_align = "top", whitespace = "break-spaces"), 
                locations = cells_body()) %>% 
   gt::tab_style(style = gt::cell_text(v_align = "top", whitespace = "break-spaces"), 
                locations = cells_stub()) 
```
